rac1 gene expression

### 2024-09-27 20240507_pharate_axonal_branching.Rmd
Dina Folder Update

ab = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/20240507_pharate_axonal_branching_Raw_Data.csv", header = T)

@@

plotdata = data.frame(x = paste(ab$Genotype, paste(ab$Sex, ab$Leg.Location)),
                      y = ab$X.Primary,
                      color = as.numeric(factor(ab$Genotype)))
plotdata = plotdata[order(paste0(ab$Sex, ab$Leg.Location)),]
plotdata$x = factor(plotdata$x, levels = c(unique(plotdata$x)))
boxplot(plotdata$y~plotdata$x, xlab="",     
        main= "",ylab="Number of Primary Branches", las = 2, cex.axis = .8)
points(x=as.numeric(factor(plotdata$x)),
       y=plotdata$y,
       cex=1,
       pch=21,
       bg=c('firebrick',"gold","darkgreen","dodgerblue")[plotdata$color])

@@

>>>>

ab = read.csv("https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/20240507_pharate_axonal_branching_Raw_Data.csv", header = T)

morph = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/20240513_pharate_axonal_morphology_Raw_Data.csv")

ab = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/UB7 - G85R Pharate Leg Axonal Branching & Mitochondria  - CSV_Branching.csv", header = T)

@@

plotdata = data.frame(x = paste(ab$Genotype, paste(ab$Sex, ab$Leg.Location)),
                      y = ab$X.Primary,
                      color = as.numeric(factor(ab$Genotype)))
plotdata = plotdata[order(paste0(ab$Sex, paste0(ab$Leg.Location, ab$Genotype))),]
plotdata$x = factor(plotdata$x, levels = c(unique(plotdata$x)))

par(mar = c(8,5,2,2))
boxplot(plotdata$y~plotdata$x, xlab="",     
        main= "",ylab="Number of Primary Branches", las = 2, cex.axis = .8)
points(x=as.numeric(factor(plotdata$x)),
       y=plotdata$y,
       cex=1,
       pch=21,
       bg=c('firebrick',"gold","darkgreen","dodgerblue")[plotdata$color])

@@

plotdata = data.frame(x = paste(ab$Genotype, ab$Sex),
                      y = ab$Avg.Mito.Branch.Length,
                      color = as.numeric(factor(ab$Genotype)))
plotdata = plotdata[order(ab$Sex),]
plotdata$x = factor(plotdata$x, levels = c(unique(plotdata$x)))
boxplot(plotdata$y~plotdata$x, xlab="",     
        main= "",ylab="Average Mitochondria", las = 2, cex.axis = .8)
points(x=as.numeric(factor(plotdata$x)),
       y=plotdata$y,
       cex=1,
       pch=21,
       bg=c('firebrick',"gold","darkgreen","dodgerblue")[plotdata$color])

plotdata = data.frame(x = paste(ab$Genotype, paste(ab$Sex, ab$Leg.Location)),
                      y = ab$Avg.Mito.Branch.Length,
                      color = as.numeric(factor(ab$Genotype)))
plotdata = plotdata[order(paste0(ab$Sex, paste0(ab$Leg.Location, ab$Genotype))),]
plotdata$x = factor(plotdata$x, levels = c(unique(plotdata$x)))

par(mar = c(8,5,2,2))
boxplot(plotdata$y~plotdata$x, xlab="",     
        main= "",ylab="Average Mitochondria", las = 2, cex.axis = .8)
points(x=as.numeric(factor(plotdata$x)),
       y=plotdata$y,
       cex=1,
       pch=21,
       bg=c('firebrick',"gold","darkgreen","dodgerblue")[plotdata$color])

plotdata = data.frame(x = paste(ab$Genotype, ab$Sex),
                      y = ab$Longest.Primary.Branch..um.,
                      color = as.numeric(factor(ab$Genotype)))
plotdata = plotdata[order(ab$Sex),]
plotdata$x = factor(plotdata$x, levels = c(unique(plotdata$x)))
boxplot(plotdata$y~plotdata$x, xlab="",     
        main= "",ylab="Longest Primary Branch", las = 2, cex.axis = .8)
points(x=as.numeric(factor(plotdata$x)),
       y=plotdata$y,
       cex=1,
       pch=21,
       bg=c('firebrick',"gold","darkgreen","dodgerblue")[plotdata$color])

plotdata = data.frame(x = paste(ab$Genotype, paste(ab$Sex, ab$Leg.Location)),
                      y = ab$Longest.Primary.Branch..um.,
                      color = as.numeric(factor(ab$Genotype)))
plotdata = plotdata[order(paste0(ab$Sex, paste0(ab$Leg.Location, ab$Genotype))),]
plotdata$x = factor(plotdata$x, levels = c(unique(plotdata$x)))

par(mar = c(8,5,2,2))
boxplot(plotdata$y~plotdata$x, xlab="",     
        main= "",ylab="Longest Primary Branch", las = 2, cex.axis = .8)
points(x=as.numeric(factor(plotdata$x)),
       y=plotdata$y,
       cex=1,
       pch=21,
       bg=c('firebrick',"gold","darkgreen","dodgerblue")[plotdata$color])

plotdata = data.frame(x = paste(ab$Genotype, ab$Sex),
                      y = ab$Shortest.Primary.Branch..um.,
                      color = as.numeric(factor(ab$Genotype)))
plotdata = plotdata[order(ab$Sex),]
plotdata$x = factor(plotdata$x, levels = c(unique(plotdata$x)))
boxplot(plotdata$y~plotdata$x, xlab="",     
        main= "",ylab="Shortest Primary Branch", las = 2, cex.axis = .8)
points(x=as.numeric(factor(plotdata$x)),
       y=plotdata$y,
       cex=1,
       pch=21,
       bg=c('firebrick',"gold","darkgreen","dodgerblue")[plotdata$color])

plotdata = data.frame(x = paste(ab$Genotype, paste(ab$Sex, ab$Leg.Location)),
                      y = ab$Shortest.Primary.Branch..um.,
                      color = as.numeric(factor(ab$Genotype)))
plotdata = plotdata[order(paste0(ab$Sex, paste0(ab$Leg.Location, ab$Genotype))),]
plotdata$x = factor(plotdata$x, levels = c(unique(plotdata$x)))

par(mar = c(8,5,2,2))
boxplot(plotdata$y~plotdata$x, xlab="",     
        main= "",ylab="Shortest Primary Branch", las = 2, cex.axis = .8)
points(x=as.numeric(factor(plotdata$x)),
       y=plotdata$y,
       cex=1,
       pch=21,
       bg=c('firebrick',"gold","darkgreen","dodgerblue")[plotdata$color])

### 2024-09-27 A4V BMP Signaling Genes Analysis.Rmd
Dina Folder Update

@@

>>>>

row.names(scaled) = bmp[row.names(scaled),1]
allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
colors = allcolors[1:branches]

@@

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M', 'TktOEWT.M'),]

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F', 'TktOEWT.F'),]

allscaled = cbind(Fhmdata,Mhmdata)
allmean = GR.mean[,colnames(allscaled)]
row.names(allmean) = bmp[row.names(allmean),1]

scaled = allscaled
Title = " "
branches=3

row.names(scaled) = bmp[row.names(scaled),1]
allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
colors = allcolors[1:branches]

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktOEGR.M'),]

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktOEGR.F'),]

allscaled = cbind(Fhmdata)
allmean = GR.mean[,colnames(allscaled)]
row.names(allmean) = bmp[row.names(allmean),1]

scaled = allscaled
Title = " "
branches=3

row.names(scaled) = bmp[row.names(scaled),1]
allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
colors = allcolors[1:branches]

```{r}

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "M",]
hmgroups = hmgroups[c('WT.M', 'GR.M', 'TktDfGR.M', 'TktDfWT.M'),]

hmgroups = GR.mean.meta[GR.mean.meta$Sex == "F",]
hmgroups = hmgroups[c('WT.F', 'GR.F', 'TktDfGR.F', 'TktDfWT.F'),]

allscaled = cbind(Fhmdata,Mhmdata)
allmean = GR.mean[,colnames(allscaled)]
row.names(allmean) = bmp[row.names(allmean),1]

scaled = allscaled
Title = " "
branches=3

row.names(scaled) = bmp[row.names(scaled),1]
allcolors=c('brown', 'gold3', 'darkgreen', 'cornflowerblue', 'mediumorchid', 'orangered')
colors = allcolors[1:branches]

### 2024-09-27 Anna qPCR data/AnnaThesisA4VRNAseqFigures.Rmd
Dina Folder Update

@@

@@

>>>>

metab.p = data.frame(KEGG =  GRxWT.C[mo, "KEGG"],
                     GRxWT.C =  GRxWT.C[mo, "p"],
                     GRxWT.Df =  GRxWT.Df[mo, "p"],
                     GRxWT.OE =  GRxWT.OE[mo, "p"],
                     GR.CxDf =  GR.CxDf[mo, "p"],
                     WT.CxDf =  WT.CxDf[mo, "p"],
                     GR.CxOE =  GR.CxOE[mo, "p"],
                     WT.CxOE =  WT.CxOE[mo, "p"])
row.names(metab.p) = mo

metab.FDR = data.frame(KEGG =  GRxWT.C[mo, "KEGG"],
                     GRxWT.C =  GRxWT.C[mo, "FDR"],
                     GRxWT.Df =  GRxWT.Df[mo, "FDR"],
                     GRxWT.OE =  GRxWT.OE[mo, "FDR"],
                     GR.CxDf =  GR.CxDf[mo, "FDR"],
                     WT.CxDf =  WT.CxDf[mo, "FDR"],
                     GR.CxOE =  GR.CxOE[mo, "FDR"],
                     WT.CxOE =  WT.CxOE[mo, "FDR"])
row.names(metab.FDR) = mo

metab.FC = data.frame(KEGG =  GRxWT.C[mo, "KEGG"],
                     GRxWT.C =  GRxWT.C[mo, "FC"],
                     GRxWT.Df =  GRxWT.Df[mo, "FC"],
                     GRxWT.OE =  GRxWT.OE[mo, "FC"],
                     GR.CxDf =  GR.CxDf[mo, "FC"],
                     WT.CxDf =  WT.CxDf[mo, "FC"],
                     GR.CxOE =  GR.CxOE[mo, "FC"],
                     WT.CxOE =  WT.CxOE[mo, "FC"])
row.names(metab.FC) = mo

@@

metab.id = data.frame(KEGG = names(metab.id),
                      metab = metab.id)

@@

PathwayID = "04146"
out.id = 'G85R_F'
FC.data = setNames(TKT.EdgeR.FC$GRxWT.FC, row.names(TKT.EdgeR.FC))
FDR.data = setNames(TKT.EdgeR$GRxWT.FC, row.names(TKT.EdgeR))

### 2024-09-27 DeficiencyScreen/ManuscriptGOtermPlot.Rmd
Dina Folder Update

fig3 <- fig2 %>% layout(xaxis = list(title = "Number of Genes"),
           yaxis = list(title = ""),
           title = "Suppressor Enriched GO Terms",
           margin = m,
           barmode = 'stack',
           shapes = list(
                         list(type = "rect",
                              fillcolor = "white", 
                              line = list(color = "black", width = 2.5), 
                              opacity = 1,
                              x0 = -30, x1 = -5, xref = "x",
                              y0 = -.5, y1 = 15.5, yref = "y",
                              layer = "below"),
                         list(type = "rect",
                              fillcolor = "white", 
                              line = list(color = "black", width = 2.5), 
                              opacity = 1,
                              x0 = -30, x1 = -5, xref = "x",
                              y0 = 15.5, y1 = 22.5, yref = "y"),
                         list(type = "rect",
                              fillcolor = "white", 
                              line = list(color = "black", width = 2.5), 
                              opacity = 1,
                              x0 = -30, x1 = -5, xref = "x",
                              y0 = 22.5, y1 = 34.5, yref = "y")
                         ))

@@

@@

@@

sigGO = Enhance.GO[c(row.names(Enh.BP.RT), 
                     row.names(Enh.CC.RT), 
                     row.names(Enh.MF.RT)), ]

@@

@@

>>>>

fig3 <- fig2 %>% layout(xaxis = list(title = "Number of Genes"),
           yaxis = list(title = ""),
           title = "Suppressor Enriched GO Terms",
           margin = m,
           barmode = 'stack',
           shapes = list(
                         list(type = "rect",
                              fillcolor = "white", 
                              line = list(color = "black", width = 2.5), 
                              opacity = 1,
                              x0 = -30, x1 = -5, xref = "x",
                              y0 = -.5, y1 = 15.5, yref = "y",
                              layer = "below"),
                         list(type = "rect",
                              fillcolor = "white", 
                              line = list(color = "black", width = 2.5), 
                              opacity = 1,
                              x0 = -30, x1 = -5, xref = "x",
                              y0 = 15.5, y1 = 21.5, yref = "y"),
                         list(type = "rect",
                              fillcolor = "white", 
                              line = list(color = "black", width = 2.5), 
                              opacity = 1,
                              x0 = -30, x1 = -5, xref = "x",
                              y0 = 21.5, y1 = 31.5, yref = "y")
                         ))

@@

fig5 <- fig4 %>% add_annotations(x = -17.5,
                        y = 18.5,
                        text = "Cellular Component",
                        showarrow = F,
                        textangle = -90,
                        font = list(size = 15))

fig6 <- fig5 %>% add_annotations(x = -17.5,
                        y = 27,
                        text = "Biological Process",
                        showarrow = F,
                        textangle = -90,
                        font = list(size = 15))

treemapPlot(Sup.CC.RT)

scatterPlot(Sup.CC.SM, Sup.CC.RT)

treemapPlot(Sup.BP.RT)

scatterPlot(Sup.BP.SM, Sup.BP.RT)

treemapPlot(Sup.MF.RT)

scatterPlot(Sup.MF.SM, Sup.MF.RT)

@@

```{r include = FALSE}

@@

sigGO = Enhancer.GO[c(row.names(Enh.BP.RT), 
                     row.names(Enh.CC.RT), 
                     row.names(Enh.MF.RT)), ]

@@

##All Suppressors
```{r}

treemapPlot(Enh.CC.RT)

scatterPlot(Enh.CC.SM, Enh.CC.RT)

treemapPlot(Enh.BP.RT)

scatterPlot(Enh.BP.SM, Enh.BP.RT)

treemapPlot(Enh.MF.RT)

scatterPlot(Enh.MF.SM, Enh.MF.RT)

@@

#Enhancers
```{r echo=F, include=F}

GO.data = Moderate.GO
GO.ontology = "BP"

Mod.BP.SM = simMatrix
Mod.BP.RT = reducedTerms
Mod.BP.RT$Freq = 1
i=1
while(i<=nrow(Mod.BP.RT)){
  Mod.BP.RT$Freq[i] =  sum(Mod.BP.RT$parentTerm == Mod.BP.RT$parentTerm[i])
  i=i+1
}
Mod.BP.RT = Mod.BP.RT[order(Mod.BP.RT$Freq, decreasing = T),]

Mod.CC.SM = simMatrix
Mod.CC.RT = reducedTerms
Mod.CC.RT$Freq = 1
i=1
while(i<=nrow(Mod.CC.RT)){
  Mod.CC.RT$Freq[i] =  sum(Mod.CC.RT$parentTerm == Mod.CC.RT$parentTerm[i])
  i=i+1
}
Mod.CC.RT = Mod.CC.RT[order(Mod.CC.RT$Freq, decreasing = T),]

Mod.MF.SM = simMatrix
Mod.MF.RT = reducedTerms
Mod.MF.RT$Freq = 1
i=1
while(i<=nrow(Mod.MF.RT)){
  Mod.MF.RT$Freq[i] =  sum(Mod.MF.RT$parentTerm == Mod.MF.RT$parentTerm[i])
  i=i+1
}
Mod.MF.RT = Mod.MF.RT[order(Mod.MF.RT$Freq, decreasing = T),]

sigGO = Repress.GO[c(row.names(Mod.BP.RT), 
                     row.names(Mod.CC.RT), 
                     row.names(Mod.MF.RT)), ]
sigGO = sigGO[row.names(sigGO)!="GO:0032991",]

fig <- plot_ly(data, 
               x = ~numDEInCat, y = ~term, 
               type = 'bar',
               name = "Candidate Modpressor Genes",
               marker = list(colorscale = list(c(0,.9,1), c("brown","gold", "steelblue")),
    reversescale =T,
                             colorbar = list(title = "-log10(FDR)",
                                      len = .8, outlinewidth = 0,
                                      tickformat = ".2f",
                                      tick0 = 0, xpad = 10),
                             color = ~Score,
                             line = list(color = "black", width = 1.5)),
    hoverinfo = "text",
    hovertext = paste("Sample:", data$term,
                      "\nGO ID: ", data$category,
                      "\nTotal DE: ", data$numDEInCat,
                      "\nTotal in Cat.: ", data$numInCat,
                      "\nFDR: ", signif(data$adjp, 3)))

fig3 <- fig2 %>% layout(xaxis = list(title = "Number of Genes"),
           yaxis = list(title = ""),
           title = "Modpressor Enriched GO Terms",
           margin = m,
           barmode = 'stack',
           shapes = list(
                         list(type = "rect",
                              fillcolor = "white", 
                              line = list(color = "black", width = 2.5), 
                              opacity = 1,
                              x0 = -30, x1 = -5, xref = "x",
                              y0 = -.5, y1 = 15.5, yref = "y",
                              layer = "below"),
                         list(type = "rect",
                              fillcolor = "white", 
                              line = list(color = "black", width = 2.5), 
                              opacity = 1,
                              x0 = -30, x1 = -5, xref = "x",
                              y0 = 15.5, y1 = 22.5, yref = "y"),
                         list(type = "rect",
                              fillcolor = "white", 
                              line = list(color = "black", width = 2.5), 
                              opacity = 1,
                              x0 = -30, x1 = -5, xref = "x",
                              y0 = 22.5, y1 = 34.5, yref = "y")
                         ))

#Moderate Suppressors
```{r}

treemapPlot(Mod.CC.RT)

treemapPlot(Mod.BP.RT)

treemapPlot(Mod.MF.RT)

### 2024-09-27 GeneExpressionBoxPlots.Rmd
update
Dina Folder Update

---
title: "Box Plots Using All Data"
author: "John Santiago"
date: "2023-11-28"
output: html_document
---

@@

library(plotly)
library(edgeR)

@@

@@

##relish FBgn0014018
##attacin FBgn0041579
##cecropin FBgn0000276
##diptericin FBgn0004240
##drosocin FBgn0010388
##defensin FBgn0010385
##drosomycin FBgn0283461
##metchnikowin FBgn0014865
##sod1 FBgn0003462
##sod2 FBgn0010213
##catalase FBgn0000261
##gstd1 FBgn0001149
## arc1 FBgn0033926

##cgs = c('CG10592','CG10827','CG1462','CG16771','CG1809','CG3264','CG3290','CG3292','CG5150','CG5361','CG5656','CG8105','CG8147')

FBgn = 'FBgn0033926'
name = ''

@@

gene$group = factor(gene$group, levels = c(unique(gene$group)))
gene$condition = factor(gene$condition, levels = c('GR.F', "TktDfGR.F", "TktOEGR.F",
                                                 'WT.F', "TktDfWT.F", "TktOEWT.F",
                                                 'GR.M', "TktDfGR.M", "TktOEGR.M",
                                                 'WT.M', "TktDfWT.M", "TktOEWT.M"))

@@

boxplot(gene$cpm~gene$condition, xlab="",     
        main= name,ylab="Counts per Million Reads", las = 2, cex.axis = .8)
points(x=as.numeric(factor(gene$condition)),y=gene$cpm,cex=1,pch=21,bg=c('firebrick',"gold","darkgreen","dodgerblue")[as.numeric(factor(gene$group))])
legend('topright',
       inset=c(-0.175,0),
       legend = c('A4V F', 'Silent F', 'A4V M', 'Silent F'), 
       fill = c('firebrick',"gold","darkgreen","dodgerblue"),
       cex = .65,
       bty = 'n',
       pt.cex = .5)

>>>>

---
title: "rac1 gene expression"
author: "John Santiago"
date: "2024-05-24"
output: html_document
---

@@

library(plotly)
library(edgeR)
library(heatmaply)
library(org.Dm.eg.db)
library(KEGGREST)

@@

nodeID = as.list(org.Dm.egENZYME)

@@

##subsetting genes for patterns

##relish FBgn0014018
##attacin FBgn0041579
##cecropin FBgn0000276
##diptericin FBgn0004240
##drosocin FBgn0010388
##defensin FBgn0010385
##drosomycin FBgn0283461
##metchnikowin FBgn0014865
##sod1 FBgn0003462
##sod2 FBgn0010213
##catalase FBgn0000261
##gstd1 FBgn0001149
## arc1 FBgn0033926
##rac1
##cgs = c('CG10592','CG10827','CG1462','CG16771','CG1809','CG3264','CG3290','CG3292','CG5150','CG5361','CG5656','CG8105','CG8147')
##mle 'FBgn0002774'
##gstD FBgn0001149
##Tudor-SN FBgn0035121
##atf4 FBgn0000370
##thor FBgn0261560
##sdhbl FBgn0030975
##ND-51L FBgn0034251
##kayak (AP-1) FBgn0001297
## Jra (AP-1) FBgn0001291
#sad FBgn0003312

##Specific enzyme
enzyme.ens = nodeID[grep('3.1.3.5',nodeID)]
enzyme.genes = GeneIDKey[GeneIDKey$ensembl %in% names(enzyme.ens)[c(1,3:5,7)],]

> GeneIDKey[intersect(s1,intersect(s2,intersect(s3,s4))),'Symbol']
 [1] "Cyp4p1"  "CG13962" "Cpr51A"  "CG11438" "Sgs5bis" "sad"    
 [7] "Lip2"    "CG4757"  "CG14229" "CG15406" "CG3270"  "CG9877" 
[13] "CG13905" "Zip71B"  "CG17027" "nom"     "CG16727" "CG9702" 
[19] "CG43740"
> GeneIDKey[intersect(s1,intersect(s2,intersect(s3,s4))),'FBgn']
 [1] "FBgn0015037" "FBgn0032824" "FBgn0033942" "FBgn0037164"
 [5] "FBgn0038523" "FBgn0003312" "FBgn0024740" "FBgn0027584"
 [9] "FBgn0031059" "FBgn0031517" "FBgn0033093" "FBgn0034819"
[13] "FBgn0035176" "FBgn0036461" "FBgn0036553" "FBgn0037617"
[17] "FBgn0038719" "FBgn0039787" "FBgn0263997"

```{r echo = F}
FBgn = 'FBgn0011817'
name = 'FBgn0011817: nmo'

@@

gene$group = factor(gene$group, levels = c(unique(gene$group)))
gene$condition = factor(gene$condition, levels = c('WT.F', "TktDfWT.F", "TktOEWT.F",
                                                   'GR.F', "TktDfGR.F", "TktOEGR.F",
                                                   'WT.M', "TktDfWT.M", "TktOEWT.M",
                                                   'GR.M', "TktDfGR.M", "TktOEGR.M"))

par(mar = c(5,7,5,2))
plot(x = NA,
      y = NA,
     type = 'n',
     ylim = c(min(gene$cpm), max(gene$cpm)),
     xlim = c(.5, 12.5),
     xaxt = "n",
     ylab="",
     yaxt = "n",
     xlab = NA)

rect(0, 0-(1.5*max(gene$cpm)), 13, 1.5*max(gene$cpm), col = 'gray95')

boxplot(gene$cpm~gene$condition, 
        xlab="",
        las = 2, 
        cex.axis = .8,
        xaxt = 'none',
        yaxt = 'none',
        boxwex = .75,
        boxlwd = 2,
        lwd = 2,
        cex.ticks = 2,
        add = T,
        col = c(rep("honeydew", 3),
                rep("thistle1", 3),
                rep("lightcyan", 3),
                rep("lightyellow", 3)))

box(lwd = 2)

points(x=as.numeric(factor(gene$condition)),
       y=gene$cpm,
       cex=1,
       pch=21,
       bg=c('firebrick',"gold","darkgreen","dodgerblue")[as.numeric(factor(gene$group))])

axis(side = 1,
     at = 1:12,
     labels = rep(c("Control", "Df", "OE"), 4),
     line = 0,
     cex.axis = .75,
     lwd.ticks = 2)

axis(side = 2,
     line = 0,
     cex.axis = 1,
     lwd.ticks = 2,
     las = 2)

axis(side = 2,
     at = .5*(max(gene$cpm) + min(gene$cpm)),
     label = "Counts per million reads",
     tick = F,
     padj = -3,
     cex.axis = 1.25)

axis(side = 1,
     at = c(2, 5, 8, 11),
     labels = c("Silent", "G85R","Silent", "G85R"),
     tick = F,
     padj = 2,
     cex.axis = 1)
axis(side = 3,
     at = c(3.5, 9.5),
     labels = c("Female", "Male"),
     tick = F,
     padj = .5,
     cex.axis = 1.5)

axis(side = 3,
     at = 6.5,
     labels = name,
     tick = F,
     padj = -1.5,
     cex.axis = 2)

axis(side = 3,
     at = c(3.5,9.5),
     tick = T,
     outer = T,
     labels = F,
     line = -2.25,
     lwd.ticks = 0)

xline1 = min(gene$cpm) - (max(gene$cpm)-min(gene$cpm))*.04
xline2 = min(gene$cpm) - (max(gene$cpm)-min(gene$cpm))*.19
lines(x=c(3.5,3.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
lines(x=c(6.5,6.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
lines(x=c(9.5,9.5), y = c(xline1, xline2), lty = 1, lwd = 2, xpd = T)
abline(v = 6.5, lty = 2, lwd = 2)

gene = data.frame(cpm = as.numeric(cpmdata[FBgn,]), 
                  condition = groups$Group, 
                  group = paste0(groups$Genotype, groups$Sex),
                  TKT = groups$TKT)

gene = gene[gene$TKT != 'OE',]

gene$group = factor(gene$group, levels = c(unique(gene$group)))
gene$condition = factor(gene$condition, levels = c('GR.F', "TktDfGR.F",
                                                 'WT.F', "TktDfWT.F",
                                                 'GR.M', "TktDfGR.M",
                                                 'WT.M', "TktDfWT.M"))

@@

boxplot(gene$cpm~gene$condition, xlab="",     
        main= name,ylab="Counts per Million Reads", las = 2, cex.axis = .8)
points(x=as.numeric(factor(gene$condition)),y=gene$cpm,cex=1,pch=21,bg=c('firebrick',"gold","darkgreen","dodgerblue")[as.numeric(factor(gene$group))])
legend('topright',
       inset=c(-0.275,0),
       legend = c('A4V F', 'Silent F', 'A4V M', 'Silent F'), 
       fill = c('firebrick',"darkgreen", "gold","dodgerblue"),
       cex = .65,
       bty = 'n',
       pt.cex = .5)
